EDA 6372 Project 1 NN

### 2021-01-20 EDA Project 1 NN 6372.Rmd
Update EDA Project 1 NN 6372.Rmd
Updated EDA.  Some exploration and commentary on missing values

>>>>

```{r}
# A closer look at some of the missing values
cars %>% filter(is.na(Number.of.Doors))
# Ferrari FF 2013 -  research indicates this has 2 doors
# Tesla Model S 2016 -  research indicates this has 4 doors
cars %>% filter(Engine.Fuel.Type=='')
# Suzuki Verona 2004 - research indicates "regular unleaded"
cars %>% filter(is.na(Engine.Cylinders))
# all Mazda RX-8/7 or electric.  Mazda RX-8 & 7 don't have cylinders
cars %>% filter(Engine.Cylinders==0) # all electric
cars %>% filter(Engine.Fuel.Type=="electric")
# there's 66 electric engines.  they all list either 0 or NA for cylinder.  Safe to put 0 I think
cars %>% filter(is.na(Engine.HP))
# a wider variety.  impute/remove?
```
